---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warnings = FALSE,
  messages = FALSE
)
```
# Teaching Culture Perception Survey (TCPS) Project

[![Build Status](https://travis-ci.org/jkaupp/tcps.svg?branch=master)](https://travis-ci.org/jkaupp/tcps)

The goal of tcps package is to provide functionality to tidy and visualize the results of running the teaching culture perception survey at an institution.

# Using the tcps package

The package is freely available and requires R to be installed as well.  R is a free open-source software available at <https://www.r-project.org/>.  It is a command line program, but there are many high quality and free interactive development environments (IDE) one can use. Rstudio <https://www.rstudio.com> is a highly recommended IDE to download and install.

To recap:

1. Download & Install R <https://www.r-project.org/>
2. Download & Install RStudio <https://www.rstudio.com>
3. Launch RStudio (which will start up an instance of R as well)

## Installation

You can install tcps from GitHub, by first installing and loading the `devtools` package

```{r gh-installation, eval = FALSE}
install.packages("remotes")

remotes::install_github("jkaupp/tcps")
```

## Using this package

There is a vignette in the package that walks through the use of the `tcps` package

```{r vignette, eval = FALSE}
vignette("using_the_tcps")
```

## Quick Features

### Importing your data

Reading in properly prepared output from survey platforms, and creating the levers.

```{r reading}
library(tcps)

# Load some sample data!
file <- tcps_sample("staff_sample.xlsx")

tcps_data <- tcps_read_excel(file)

head(tcps_data)

```

### Visualizing Levers & Scales

Provides functions to visualize the TCPS levers....

```{r rideline, fig.width = 10, fig.height = 5}
tcps_lever_ridgeline(tcps_data, name = "Prestigious Institution", lever = "lever1")
```

as well as functionality to visualize the scales/questions that comprise the lever.

```{r scale1, fig.width = 8, fig.height = 8}
tcps_lever_scale(tcps_data, choice =  "lever1", name = "Prestigious Institution")
```

## Summary Statistics

You can obtain simple summary statistics by scale, survey type, lever and question.

```{r stats, fig.width = 8, fig.height = 8}
tcps_summary_stats(tcps_data)
```


## Reporting

There is also functions to produce a boilerplate word document report (across all groups: Staff, Faculty and Students) simply by providing a path to a directory where each prepared file resides.

```{r report, eval = FALSE}

path <- dirname(tcps_sample("faculty_sample.xlsx", full.names = TRUE))

tcps_report(path_to_data = path, name_of_school = "Prestigious Institution", format = "word")

```


## Using the GUI

To help with those new to R, a GUI interface application (built with the `shiny` package) can be used by calling `tcps_gui()` at the command line after loading the `tcps` package. 
