---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warnings = FALSE,
  messages = FALSE
)
```
# Teaching Culture Perception Survey (TCPS) Project

The goal of tcps package is to provide functionality to tidy and visualize the results of running the teaching culture perception survey at an institution.

## Installation

You can install tcps from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jkaupp/tcps")
```

## Using this package

There is a vignette in the package that walks through the use of the `tcps` package

```{r vignette, eval = FALSE}
vignette("using_the_tcps")
```

## Quick Features

### Importing your data

Reading in properly prepared output from survey platforms, and creating the levers.

```{r reading}
library(tcps)

# Load some sample data!
file <- tcps_sample("staff_sample.xlsx")

tcps_data <- tcps_read_excel(file)

head(tcps_data)

```

### Visualizating Levers & Scales

Provides functions to visualize the TCPS levers....

```{r rideline, fig.width = 10, fig.height = 5}
tcps_lever_ridgeline(tcps_data, name = "Prestigous Institution", lever = "lever1")
```

as well as functionality to visualize the scales/quesitons that comprise the lever.

```{r scale1, fig.width = 8, fig.height = 8}
tcps_lever_scale(tcps_data, choice =  "lever1", name = "Prestigous Institution")
```

## Summary Statistics

You can obtain simple summary statistics by scale, survey type, lever and question.

```{r stats, fig.width = 8, fig.height = 8}
tcps_summary_stats(tcps_data)
```


## Reporting

There is also functions to produce a boilerplate word document report (across all groups: Staff, Faculty and Students) simply by providing a path to a directory where each prepared file resides.

```{r report, eval = FALSE}

path <- dirname(tcps_sample("faculty_sample.xlsx", full.names = TRUE))

tcps_report(path_to_data = path, name_of_school = "Prestigous Institution", format = "word")

```
